BERT Model Compression and Weight Sharing

### 2019-05-11 paper/paper.tex
Model and experimental setup

We distort via \[
\rankreduce(\bvartheta) = \tilde U \tilde \Sigma \tilde V^\top,
\]
where $\tilde U, \tilde \Sigma, \tilde V$ are conforming matrices such that the
smallest values on the spectrum $\Sigma$ is zeroed out, as well as corresponding
values in $U,V$. If we keep only the $r$ largest spectral values, then we store
$\tilde U \tilde \Sigma$, an $n\times r$ matrix, and $\tilde V$, an $m\times r$
matrix. Thus, instead of storing $2nm$ floats, we may store $r(n+m)$, achieving
a compression rate of \[
\rho = \frac{r(n+m)}{2mn}.
\]
Note however, that storing matrices in this manner requires an additional
matrix multiplication in evaluation time, since we have to compute the product
$\tilde U \tilde \Sigma \tilde V$.

@@

\section{Methods}

\begin{itemize}
\item What are the exact details of the dataset that you used? (Number of data points / standard or non-standard / synthetic or real / exact form of the data)

\item What are the exact details of the features you computed?

\item How did you train or run inference? (Optimization method / hyperparameter settings / amount of time ran / what did you implement versus borrow / how were baselines computed).

\item What are the exact details of the metric used?
\end{itemize}

>>>>

We distort via \[
\rankreduce(\bvartheta; r) = \tilde U \tilde \Sigma \tilde V^\top,
\]
where $\tilde U, \tilde \Sigma, \tilde V$ are conforming matrices such that the
smallest values on the spectrum $\Sigma$ is zeroed out, as well as corresponding
values in $U,V$. If we keep only the $r$ largest spectral values, then we store
$\tilde U \tilde \Sigma$, an $n\times r$ matrix, and $\tilde V$, an $m\times r$
matrix. Thus, instead of storing $2nm$ floats, we may store $r(n+m)$, achieving
a compression rate of \[
\rho = \frac{r(n+m)}{2mn}.
\]
Note however, that storing matrices in this manner requires an additional
matrix multiplication in evaluation time, since we have to compute the product
$\tilde U \tilde \Sigma \tilde V$.

@@

\section{Methods}
In this section, we briefly discuss our experimental setup. We mostly
work with
SST-2, a binary sentiment classification task in the GLUE multitask benchmark
framework \citep{wang2018glue}. We also validate the model's
performance with trial on the Quora Question Pair (QQP) task, which is a
binary classification task for whether two questions are equivalent. We
train with a maximum sequence length of 64 and batch size of 32 on the
NC-6 and NC-12 virtual machines on Microsoft Azure. We use the basic 
\texttt{BERT-base-uncased} model for our experimental results. We employ
early stopping in training, with patience of 1 epoch, and early stopping is
guided by validation error.

\subsection{DeepTwist}
We implement the DeepTwist framework with default frequency of distortion
every 10 batches. Additionally, we ensure that training ends on a
distortion step, so that the model produced by training has compression
benefits. For $\prune$ and $\diffprune$ distortions, we use a single
pruning rate held fixed throughout training.

\subsection{Knowledge Distillation}
For knowledge distillation experiments, we use various configurations of
the student network:
\paragraphdot{LSTM} We use a one-layer LSTM network with hidden dimension
$H=200$. We first embed the one-hot representation of tokens, and we feed
the embeddings through an LSTM. We then map the last hidden state of the
LSTM through a linear layer for classification. 
\paragraphdot{CNN} We use an implementation\footnote{\url{https://github.com/jfilter/cnn-text-classification-pytorch/blob/master/cnn_text_classification/model.py}} 
of \citet{kim2014convolutional} with kernel sizes $(3,4,5)$, hidden size
$H=300$, no dropout, and $20$ kernels for each kernel size.\footnote{These
are default in the implementation we used.}

For each model, we initialize the embedding layer of the model with the
first $H$ dimensions of the corresponding embedding layer in pretrained
BERT.
